%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\begin{acknowledgements}
\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
\vspace*{2cm}
This M.Tech \rType is the result of hard work, upon which many people have contributed and given their support. I
have made this dissertation on the topic \textbf{"\ReportTitel ."} I have also tried my best in this dissertation to
explain all the related detail. I would like to express my sincere gratitude towards my Superviser \textbf{
	\Supervisor}, Department of \depS, for providing excellent guidance, encouragement, inspiration, and constant and
timely support throughout this \DegreeS \  dissertation work. He taught me how to pursue the right aim towards the work
, and showed me differnt ways to approach the research problem. His wide knowledge and logical ways of thinking have
been great value for me, and his understanding and guidance have provided the successful completion of the
Dissertation work.

First and foremost, I would like to express my gratitude to our beloved Dean of the Computational Sciences,
Information and Communication Technology and Head of Department of Computer Science and Information Technology \textbf{\HodName},
for providing his kind support in various aspects. A special thanks to all the Respected Teachers
\textbf{\Facone}, \textbf{\Factwo}, and \textbf{\Facthree}, of the Department of Computer Science and Information
Technology.

I am always grateful to the university, our Hon’ble Vice chancellor \textbf{\Vc} for providing
such a good research environment.

	Special thanks to Ph.D scholar, especially \textbf{Ritika Singh}, \textbf{Surbhi Kumari}, \textbf{Ibrahim Momin},
\textbf{Naushad Ahmad} and  my friends \textbf{Tej Prakash}, \textbf{Gajendra Patel}, \textbf{Abhijeet Kumar},
\textbf{Amod Kumar}, \textbf{Rana Kumar}, \textbf{Krishna Murari}, \textbf{Rajan Kumar}, \textbf{Suraj}, \textbf{Md.
Aamir Sohail}, \textbf{
	Shahzeb Khan},
and all my lovely juniors  for their invaluable feedbacks, care, and moral support during this endeavor.

	\textbf{Mother} and \textbf{Father}, it is impossible to thanks adequately for everything you have done, from
loving me unconditionally to rising me in a stable household, where your persistent efforts and traditional values
taught your children to celebrate and embrace life. I could not have asked for better parents or role-models. You
showed me that anything is possible with faith, hard work and determination. 


\vspace*{0.7cm}

\setlength\tabcolsep{0pt}
\def\arraystretch{0}
\begin{table}[h]
\begin{center}
\begin{tabular}{r  r}
   \begin{minipage}{0.5\textwidth}
\begin{flushleft}
\vspace*{1cm}

\textbf{\fAuthor}\\
\textbf{(\fAID)}\\
\textbf{\DegreeS(CSE)}\\[.1cm]
\end{flushleft}
\end{minipage}
&
\begin{minipage}{0.5\textwidth}
\begin{flushleft}



\end{flushleft}
\end{minipage}
\noindent
\\
\end{tabular}
%\label{tab1}
\end{center}
\end{table}

\end{acknowledgements}
